Fitness traits of deoxynivalenol and nivalenol-producing Fusarium graminearum species complex strains from wheat

### 2017-12-20 data.Rmd
new style
Several changes including .doc as output
Added OSF link
Small changes

The data were obtained from five different (mostly repeated in time) experiments, and were organized in a single `xlsx` file. Data from each experiment are in a separate sheet and were exported to a `csv` file.

The data are already organized in a rectangular (tidy) format, mostly in the long-format (a raw is an observation), but some are in the wide (observations in multiple colums), and so will need some wrangling. This munging is done within the respective section of the data analysis page, after data import.

@@

The data are stored in the `data` folder of the GitHub repository.

https://github.com/phytopathology/paper-FGSC-fitness/data

>>>>

The data for this study were obtained from five different (mostly repeated in time) experiments, and were organized in a single `xlsx` file. Data from each experiment are in a separate sheet and were exported to a `csv` file. They are already organized in a rectangular (tidy) format, mostly in the long-format (a raw is an observation). For some experiments, they are in the wide format (observations in multiple colums), and so will need some wrangling. This munging is done within the respective section of the data analysis page, after data import.

@@

> The data are stored in the following repositories:

https://github.com/phytopathology/paper-FGSC-fitness/tree/master/dat  
https://osf.io/c2mbr/ 
Identifier: DOI 10.17605/OSF.IO/C2MBR

### 2017-12-20 index.Rmd
Small changes

<img src = "https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/PublishingImages/Fusariumdiscyclesm.jpg" align= right width = 270> This research compendium  contains the data and the commented R codes for analyzing and visualizing these data obtained from a series of experiments conducted as an MSc research in the Del Ponte lab.

The main objective was to assess and compare members of a species complex (FGSC), with varying toxigenic potential, which cause [Fusarium head blight (FHB) or scab](https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/Pages/Fusarium.aspx). FHB is an important disease of wheat and barley worldwide. Several fitness-related traits were compared in five experiments conducted both *in vitro* and in *planta*. Check the manuscript page.

@@

Please cite this research compendium as:

> Del Ponte EM. Fitness-related traits of Fusarium graminearum species complex: a research compendia. Online at https://phytopathology.github.io/paper-FGSC-fitness/

>>>>

<img src = "https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/PublishingImages/Fusariumdiscyclesm.jpg" align= right width = 270> This research compendium  contains the data and R codes for analyzing and visualizing these data obtained from a series of experiments conducted as an MSc research in the Del Ponte lab. The main objective was to assess and compare members of a species complex (FGSC), with varying toxigenic potential, which cause [Fusarium head blight (FHB) or scab](https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/Pages/Fusarium.aspx). Several fitness-related traits were compared in five experiments conducted both *in vitro* and in *planta*. Check the manuscript page.

> Del Ponte EM. Fitness-related traits of *Fusarium graminearum* species complex: a research compendia. Online at https://phytopathology.github.io/paper-FGSC-fitness/

## Pre-print version

> BIORXIV/2017/235895
Fitness traits of deoxynivalenol and nivalenol-producing *Fusarium graminearum* species complex strains from wheat
Camila P Nicolli, Franklin J Machado, Pierri Spolti, and Emerson M Del Ponte  
https://doi.org/10.1101/235895

@@
